A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
minor fixes on the report.

\subsection{C4.5}

@@

The error rate produced by Aleph when evaluating the test data was 20.45\%.
18881882 clauses were built, taking around 5 hours for the whole training
data. Despite the number of clauses, most of them are irrelevant, directly
classifying examples where no more general rule is available. Listing 
\ref{ilp_clauses} lists the most relevant clauses produced.

>>>>

As can be seen from the table, the numerical ID3 outperforms the standard ID3 in
accuracy but takes longer to compute the decision tree. The decision tree
produced is very large, as ID3 doesn't support pruning (see section 
\ref{sec:4.5}), and so is omitted from this report.

\subsection{C4.5}
\label{sec:c4.5}

@@

The error rate produced by Aleph when evaluating the test data was 20.45\%.
18881882 clauses were built, taking around 5 hours for the whole training
data. Despite the number of clauses, most of them are irrelevant, directly
classifying examples when no more general rule is available. Listing 
\ref{ilp_clauses} lists the most relevant clauses produced.
